### 2015-01-15 src/analysis.Rnw
analysis

While computing the test cases, we also collect assertion number each
test case has. We compute this as the number of asserts in the test case
incremented by one to account for test cases without any asserts. Thus the
compute both the assertions from non-redundant test cases for the mutant
selection, and also the assertions for the full set of killing test cases
for the mutant selection.

The \textit{test utility} is computed as the difference between the number
of non-redundant test cases the mutant selection achieved and the number of
non-redundant test cases of a random sample of same number of mutants.
The result is reported as a percentage of the non-redundant tests of the random
sample (the baseline).

Similarly \textit{assert utility} of a strategy is computed

>>>>

While computing the test cases, we also collect assertion information each
test case has. We compute this as the number of asserts in the test case
incremented by one to account for test cases without any asserts. Thus we
compute both the assertions from non-redundant test cases for the mutant
selection, and also the assertions for the full set of killing test cases
for the mutant selection.

The \textit{test utility} is computed as the difference between the number
of non-redundant test cases the mutant selection achieved and the number of
non-redundant test cases of a random sample of same number of mutants.
The result is reported as a percentage of the non-redundant tests of the random
sample which is taken as the baseline.

Similarly \textit{assert utility} of a strategy is computed as the difference
between the number of assertions of non-redundant test cases the mutatnt
selection achieved and the number of assertions the test cases for random
sample of same number of mutants. As before, it is reported as a percentage of
the asserts of the non-redundant tests of the random sample which is taken
as the baseline.

\textit{Strategy effectiveness} is computed by collecting all the test cases
that detected any of the mutants in the selected subset, and applying these
test cases to the complete set of mutants. The mutation score thus obtained
is then divided by the original number of detected mutants.

Similarly \textit{baseline effectiveness} is computed by getting the number
of mutants selected by the strategy, and selecting the same number of mutants
randomly, collecting the test cases that kill any of these mutants, and
applying the same test cases against the original set of mutants. The result
is then divided by the original number of detected mutants.
